GMSE: a general tool for management strategy evaluation

### 2017-09-14 notebook/presentation/GMSE_presentation.Rmd
More progress

## Introduction

@@

## Management Strategy Evaluation

@@

## Uncertainty

@@

@@

- People with strongly held views clash over objectives
- Negative effect on sustainability, biodiversity, and human livelihood

@@

@@

@@

>>>>

<!---
https://welikia.org/
http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text
https://welikia.org/explore/mannahatta-map/

--->

<center>

![](mannahatta.jpg)

</center>

![](food_biodiversity.png)

![](wicked_modelling.png)

@@

<center>

@@

</center>

## Uncertainty in natural resource management

Uncertainty is fundamental in ecological and economic systems, and their measurement

**Natural resources**: Structural and demographic uncertainty

**Resource observation**: Observation uncertainty

**Management**: Implementation uncertainty

**Stake-holder actions**: Pay-off uncertainty

@@

<!--- Transition from global to local scale --->

@@

- People with strongly held views clash over objectives
- Negative effect on sustainability, biodiversity, and human livelihood
- MSE does not integrate the livelihood decisions of people

@@

## Iterated Prisoner's dilemma rules {.smaller}

![](payoff_matrix_sm.png)
**General structure of Prisoner's dilemma scenario**

![](pd_pays.png)
**Specific payoffs satisfying a Prisoner's dilemma scenario**

## Use of genetic algorithms {.smaller}

**Each locus is an focal player's choice given an opponent's past three choices (plus one choice of first move)**

<hr>

|                  | **CCC** | **CCD** | **CDC** | **CDD** | **DCC** | **DCD** | **DDC** | **DDD** | **1st** |
|------------------|---------|---------|---------|---------|---------|---------|---------|---------|---------|
| **Strategy 1**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **Strategy 2**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **...**          |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |
| **Strategy N-1** | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **Strategy N**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |

<hr>

**Total of 512 possible strategies**

## Use of genetic algorithms {.smaller}

```{r, echo=FALSE}
inputPanel(

  numericInput("CC", label = "CC", 0, width="30%"),
  numericInput("DC", label = "DC", 0, width="30%"),
  numericInput("CD", label = "CD", 0, width="30%"),
  numericInput("DD", label = "DD", 0, width="30%"),

  style='width: 2000px; height: 60px'
)
```

```{r, echo=FALSE}
gres <- reactive({ 
     cc <- input$CC;
     dc <- input$DC;
     cd <- input$CD;
     dd <- input$DD;
     rd <- 100;
     gn <- 100;
     co <- 0.05;
     mu <- 0.05;

     game_res <- games_ga(CC = cc, DC = dc, CD = cd, DD = dd, rounds = rd,
                          generations = gn, cross_prob = co, 
                          mutation_prob = mu, num_opponents = 100);     
     all <- c(game_res$genos, "break_1",
              rownames(game_res$genos), "break_2",
              game_res$fitness);
    })
```

```{r, echo = FALSE}
renderPlot({
    break2    <- which(gres()=="break_2")[1]+1;
    end       <- length(gres());
    fitnesses <- gres()[break2:end];
    fitnesses <- as.numeric(fitnesses);
    mean_fit  <- fitnesses / (100 * 100);
    maxpt     <- max(c(input$CC, input$CD, input$DC, input$DD));
    par(mar=c(5,5,1,1));
    plot(x = 1:length(mean_fit), y=mean_fit, type="l", ylim=c(0,maxpt), lwd = 3,
        xlab="Generation", ylab = "Mean strategy fitness per round",
         cex.axis=1.5, cex.lab=1.5);
})
```

## Adaptive strategies simulated {.smaller}

```{r, echo=FALSE}
renderTable({
      break1   <- which(gres()=="break_1")[1] - 1;
      break2   <- which(gres()=="break_2")[1] - 1;
      geno_vec <- gres()[1:break1];
      geno_row <- gres()[(break1+2):break2];
      genos    <- matrix(data =  geno_vec, ncol = 10, byrow = FALSE);
      rownames(genos) <- geno_row;
      colnames(genos) <- c("CCC", "CCD", "CDC", "CDD", "DCC", "DCD", "DDC",
                           "DDD", "1st", "Final %");
      final_table <- genos[1:10,];

}, include.rownames=TRUE)
```

@@

<center>

@@

</center>
